---
title       : Flight Statistics
subtitle    : Finding out which airlines performs better
author      : Roy
job         : Coursera Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Why Flight Statistics?

* FiveThirtyEight is one of my favorite website, I came across an article about Best Airline.
* This is pretty intresting and I have downloaded the data and build my own version on shiny
* I have trimmed down the data to just 12 major airports
* The data I used in the application is March 2014 from Bureau of Transportation Statistics

--- .class #id 

## What does it do?

* User can select the "from" and "to" airport on the sidebar
* The application will automatically trim down the data and create a boxplot for all airline

--- .class #id 

## How to make this? (UI)

* Building the UI - the sidebar
```{r, eval=FALSE}
# Select boxes
selectInput("from", label = h3("From Airport"), choices = airports, selected = 1),
selectInput("to", label = h3("To Airport"), choices = airports, selected= 1)
```

* Building the UI - the main panel
```{r, eval=FALSE}
# Title bar and the boxplot
textOutput("title"),  
hr(),
plotOutput("boxPlot")
```

--- .class #id 

## How to make this? (Server)
* Load the data
```{r, eval=FALSE}
# Get the airport code to airport name data
airports <- read.csv("L_AIRPORT_ID.csv",na.string="")
#Load the actual data
data <- read.csv("705002017_T_ONTIME_2014_3.csv",na.string="")     
```

* Get the input, filter the data and redraw the boxplot
```{r, eval=FALSE}
 trim <- data[data$ORIGIN_AIRPORT_ID==input$from & data$DEST_AIRPORT_ID==input$to,]
if(nrow(trim)==0){
output$title <- renderText(paste("No flight from ",
airports[airports$Code==input$from,]$Description , " -to-> ",
airports[airports$Code==input$to,]$Description ))                               
}else{
output$title <- renderText(paste("Statistics of flight from ",
airports[airports$Code==input$from,]$Description , " -to-> ",
airports[airports$Code==input$to,]$Description))                               
boxplot(ACTUAL_ELAPSED_TIME~CARRIER,data=trim, main="Flight time against each airline", 
ylab="Actual Elapsed Time in minutes", xlab="Airline")
}
```

--- .class #id 
## The result

* Not all the airline got flight between any 2 of the airport
* The boxplot shows the average time of all flight
* Even it is the same flight, there are some differences between different airlines.
* The actual flying time has a wide distribution, meaning it is very hard to predict the flight time.


